\bibliographystyle{plain}
\bibliography{biblio}

\begin{thebibliography}{11}
	
	\bibitem{}
		Abreu, Dillip, \& Brunnermeier, M. K. (2.003). \emph{Bubbles and Crashes}. Econometrica. 

	\bibitem{}
		Aliber, R. (2.012, Junio). Bubbles, Crises, and the Global Economic Outlook [Video]. Recuperado de \url{www://http.youtube.com/watch?v=kJARAXN2Pk0}.

	\bibitem{}
		Ampliaciones de capital | matematicas-financieras.com [Web log post]. (2.013). Recuperado de \url{http://www.matematicas-financieras.com/Ampliacion-de-Capital-I-P53.htm} 	

	\bibitem{}
		Apalancamiento financiero | Gerencie.com [Web log post]. (2013). Recuperado de \url{http://www.gerencie.com/apalancamiento-financiero.html}.

	\bibitem{}
		Barlevy, G. (2.007). \emph{Economic theory and asset bubbles}. Recuperado de \url{http://papers.ssrn.com/sol3/papers.cfm?abstract\_id=1012865}
		
	\bibitem{}
		Bhattacharya, U., \& Yu, X. (2.005). The Causes and Consequences of Recent Financial Market Bubbles: An Introduction. \emph{Kelley School of Business, Indiana University}. doi:0.1093/rfs/hhn008

	\bibitem{}
		Bierman, H. (1.991). The Great Myths of 1929 and the Lessons to be Learned. \emph{Greenwood Press}. 

	\bibitem{}
		Blanchard, O. (1.979) \emph{Speculative Bubbles, Crashes, and Rational Expectations}. Economic Letters.

	\bibitem{}
		Blanchard, O., \& Watson, M. (1.982). \emph{Bubbles, Rational Expectations and Financial Markets}. 
	
	\bibitem{}
		Blunt, W. (1.950). \emph{Tulipmania}. 	 

	\bibitem{}
		Brandenburguer, A. M., \& Harbone, W. S. (1.996). Value-Based Business Strategy. \emph{Management Economics and Strategy}.

	\bibitem{}
		Blustein, P. (2.009). \emph{Misadventures of the Most avored Nations: Clashing Egos, Inflated Ambitions, and the Great Shambles of the World Trade System}. 

	\bibitem{}
		Bubbles, Bubbles The Economic Collapse Bubble - Episode 75 [Video]. (2.013, mayo 29). Recuperado de \url{http://www.youtube.com/watch?v=29ZN7LFEcOI}

	\bibitem{}
		Capital autorizado, suscrito y pagado | Gerencie.com [Web log post]. (2.013). Recuperado de \url{http://www.gerencie.com/capital-autorizado-suscrito-y-pagado.html}

	\bibitem{}
		Carolus Clusius. (2.013). \emph{In Sir Thomas Browne}. Recuperado de \url{http://penelope.uchicago.edu/~grout/encyclopaedia\_romana/aconite/clusius.html}

	\bibitem{}
		Carswell, J. (1.993). The South Sea Bubble. 

	\bibitem{}
		Castaing (1.720, agosto 26). Freke’s Prices of Stocks. \emph{The Course of the exchange}. 	

	\bibitem{}
		Chang, R., \& Velasco, A. (n.d.). Liquidity Crises in Emerging Markets: Theory and Policy. \emph{National Bureau of Economic Research, 72}. 

	\bibitem{}
		Cochrane, J. H. (2.001). Book Review of `Famous First Bubbles´. \emph{Journal of Political Economy 109, 5}, 1150–4. 	

	\bibitem{}
		Corsetti, G., Pesenti, P., \& Roubini, N. (1.998). What Caused the Asian Currency and Financial Crisis? \emph{National Bureau of Economic Research. NBER Working Paper}. 

	\bibitem{}
		Coss, P. (n.d.). \emph{Verzameling van een meenigte tulipaanen}. Wageningen University	\footnote{Este libro se encuentra en los Países Bajos en la \emph{Krelage Collection} de la Universidad de Wageningen y más concretamente en el Centro de Investigación de la Biblioteca. Es tan sólo uno de sólo cuarenta y tres libros sobre el tulipán que se sabe que existen. De estos cuarenta y tres, treinta y cuatro se redactaron en los Países Bajos. Se trata, esencialmente, de manuscritos o de acuarelas recopiladas.}

	\bibitem{}
		\emph{Cultura general : Cliente Ninja | Propiedad Privada}. (2013). Recuperado de \url{http://www.propiedadprivada.com/cultura-general-cliente-ninja/415/}

	\bibitem{}
		Dale, R. S., Johnson, J. E., \& Tang, L. (2.005). Financial markets can go mad: evidence of irrational behaviour during the South Sea Bubble. \emph{Economic History Review}, 233–271.	

	\bibitem{}
		Damodaran, A. (n.d.). \emph{Stern School of Business}. Recuperado de \url{http://people.stern.nyu.edu/adamodar/pdfiles/country/LBO.pdf}

	\bibitem{}
		Dash, M. (1.999). \emph{Tulipmania}. 

	\bibitem{}
		DeMarzo, P., Kaniel, R., \& Kremer, I. (2.007). \emph{Relative Wealth Concerns and Financial Bubbles. Review of Financial Studies}. 

	\bibitem{}
		Diamond, P. (1.965). The American Economic Review. 

	\bibitem{}
		Diccionario de la lengua española Real Academia Española. (2.013). Recuperado de \url{http://lema.rae.es/drae/?cal=titulizar}

	\bibitem{}
		Dinero fiduciario | Gerencie.com [Web log post]. (2.013, febrero 26). Recuperado de \url{http://www.gerencie.com/dinero-fiduciario.html}

	\bibitem{}
		Dooley, M. (1.999). Origins of the Crisis in Asia. \emph{Boston: Kluwer Academic Publishers}. 

	\bibitem{}
		Dutch tulip mania documentary - [Video]. (2.012, diciembre 31). Recuperado de \url{http://www.youtube.com/watch?v=OgF6HwbmJ2c}

	\bibitem{}
		Dutot, N. (1.935). \emph{Rèflexions politiques sur les finances et le commerce}. 

	\bibitem{}
		Estado de flujos de efectivo | Gerencie.com [Web log post]. (2.010, junio 12). Recuperado de \url{http://www.gerencie.com/estado-de-flujos-de-efectivo.html}

	\bibitem{}
		Federal reserve bank of San Francisco (2.004). House Prices and Fundamental Value. 	

	\bibitem{}
		Fisher, K., \& Statman, M. (2.002). \emph{Blowing Bubbles}. The Journal of Psychology and Financial Markets.

	\bibitem{}
		Franklin Templeton Strategic (2.013, febrero). Recuperado de \url{http://www.franklintempleton.com.es/downloadsServlet?docid=hhk35xvf}

	\bibitem{}
		Galbraith, J. (1.954). \emph{The Great Crash 1929}. Boston: Houghton Mifflin Company. 

	\bibitem{}
		Garber, P. (1.986). The Tulipmania Legend. \emph{Center for the Study of Futures Markets}. 

	\bibitem{}
		Garber, P. (1.989). Tulipmania. \emph{The Journal of Political Economy, 97(3), 535-560}.  	

	\bibitem{}
		Garber, P. (2.000). \emph{Famous First Bubbles: The Fundamentals of Early Manias}. Cambridge. MA: The MIT Press.
	
	\bibitem{}
		Gennotte, G., \& Leland, H. (1.990). Market Liquidity, Hedging, and Crashes. \emph{American Economic Review}.

	\bibitem{}
		Gibney, A. (Director). (2.005). \emph{Enron: The Smartest Guys in the Room [Película]}. Estados Unidos. 

	\bibitem{}
		Gibney, A. (Director). (2.005). \emph{Enron: The Smartest Guys in the Room [Película]}. Estados Unidos. 

	\bibitem{}
		Goetzman, W., \& Beineck, E. J. (2013, octubre 29). Reinterpreting the First Great Stock Market Crash: South Sea, Mississippi \& Windhandel Bubbles [Video]. Recuperado de \url{http://www.youtube.com/watch?v=ZVkl\_zjqCdU}

	\bibitem{}
		Grossman, G., \& Yanagawa, N. (1.992). Asset Bubbles and Endogenous Growth. \emph{Journal of Monetary Economics}. 

	\bibitem{}
		Hamilton, J. (1.987). Monetary Factors in the Great Depression. \emph{Journal of Monetary Economics, 19, 145-169}. 

	\bibitem{}
		Henry Thornton - Blog [Web log post]. (n.d.). Recuperado de \url{http://www.henrythornton.com/blog.asp?blog\_id=1741}

	\bibitem{}
		Hepburn , H. (2.012, febrero 19). Mississippi Bubble: The building of John Law’s Empire [Web log post]. Recuperado de \url{http://mississippibubble101.blogspot.co.at/2013/02/the-building-of-john-laws-empire.html}

	\bibitem{}
		Hutcheson, A. (1.720). \emph{Collection of Calculations and Remarks Relating to the South Sea Scheme}. Londres.	
	\bibitem{}
		\emph{Importancia de los Medios de Comunicación}. (2.013). Recuperado de \url{http://www.importancia.org/medios-de-comunicacion.php}

	\bibitem{}
		Gaceta d'Amsterdam. (1.719). \emph{Amsterdamse Courant}.  	

	\bibitem{}
		García Montalvo, J., \& Raya Vilchez, J. M. (2.012). What is the right price of Spanish residential real estate? \emph{SEFO - Spanish Economic and Financial Outlook}. 

	\bibitem{}
		Goldgar, A. (2.007). Tulipmania: Money, Honor, and Knowledge in the Dutch Golden Age. \emph{Chicago University Press, 49}. 	

	\bibitem{}
		\emph{Importancia de los Medios de Comunicación}. (2.013). Recuperado de \url{http://www.importancia.org/medios-de-comunicacion.php}

	\bibitem{}
		Juan, J. (2.011). \emph{Nada es gratis}. Destino. 

	\bibitem{}
		John Law and the Mississippi Bubble [Video]. (2.010, octubre 15). Recuperado de \url{http://www.youtube.com/watch?v=diEVmQZ1QfM}

	\bibitem{}
		John law economist history of speculation bubbles [Video]. (2.012, noviembre 27). Recuperado de \url{http://www.youtube.com/watch?v=4KNW9o7wG3g}

	\bibitem{}
		Keynes, J. (1.935). \emph{The General Theory of Employment, Interest, and Money}.

	\bibitem{}
		Kindleberger, C. (1.996). \emph{Manias, Panics and Crashes: A History of Financial Crises}.  

	\bibitem{}
		King, I., \& Ferguson, D. (1.993). \emph{Dynamic inefficiency, endogenous growth, and Ponzi games}.  

	\bibitem{}
		Kiladze, T. (2012, mayo 26). Why do we keep falling for economic bubbles - and will we ever learn? \emph{The Globe and Mail}. 

	\bibitem{}
		Krugman, P. (1.994). \emph{The Myth of Asia´s Miracle. Foreign Affairs}. 

	\bibitem{}
		Krugman, P. (2.000). \emph{El retorno de la economía de la depresión}. 

	\bibitem{}
		Leverage (finance) - Wikipedia, the free encyclopedia. (n.d.). Recuperado diciembre 28, 2.014, from \url{http://en.wikipedia.org/wiki/Leverage\_28finance29}

	\bibitem{}
		 Speake, J. (2.003) \emph{Literature of Travel and Exploration: A to F}. New York

	\bibitem{}
		Lüthy, H. (1.961). \emph{La Banque protestante en France de la rèevocation de l’Édit de Nantes á la Rèvolution}. Paris. 	

	\bibitem{}
		Lythberg, B. (2.010). \emph{The Tulip Anthology}. 	

	\bibitem{}
		Mackay, C. (1.841). \emph{Extraordinary Popular Delusions and the Madness of Crowds}. New York: Harmony. 

	\bibitem{}
		Malkiel, B. (2.007). \emph{A random Walk Down Wall Street: the time tested strategy for successful investment}. 
	\bibitem{}
		Malkiel, B. (2.010). Bubbles in Asset Prices. \emph{Princeton University CEPS, 200}. 

	\bibitem{}
		Market timing. (n.d.). In Wikipedia, the free encyclopedia. Recuperado del 5 de noviembre, 2.013, de \url{http://en.wikipedia.org/wiki/Market\_timing}

	\bibitem{}
		Marshall, D. (1.998). Understanding the Asian Crisis: Systemic Risk as Coordination Failure. \emph{Federal Reserve Bank of Chicago, Economic Perspective Third Quarter, 13-28}. 

	\bibitem{}
		Maurits van der Veen, A. (2.009). The Dutch Tulip Mania: The Social Politics of a Financial Bubble. 	

	\bibitem{}
		Mayer, M. (2.013). Housing Bubbles: A Survey. \emph{Columbia Business School}. Recuperado de www.annualreviews.org

	\bibitem{}
		Missel, L. (n.d.). \emph{Dutch Tulip History}. Wageningen University. 	

	\bibitem{}
		Neal, L. (1.999). The rise of Financial Capitalism. \emph{Cambridge University Press}.

	\bibitem{}
		Neal, L., \& Atack, J. (2.007). \emph{The Origins and Development of Financial Markets and Institutions}. Cambridge: Cambridge University. 	 

	\bibitem{}
		Neira, N. (2.008, septiembre 7). Valor presente neto | Gerencie.com [Web log post]. Recuperado de \url{http://www.gerencie.com/valor-presente-neto.html}
	

	\bibitem{}
		Ogier Ghiselin de Busbecq. (2013). \emph{In Sir Thomas Browne}. Recuperado de \url{http://penelope.uchicago.edu/~grout/encyclopaedia\_romana/aconite/busbecq.htm}

	\bibitem{}
		O’Hara, M. (2.012). Bubbles: Some Perspectives (and Loose Talk) from History. \emph{Johnson Graduate School of Management, Cornell University}. Recuperado de \url{http://rfs.oxfordjournals.org}

	\bibitem{}
		Pavord, A. (1.999). \emph{The Tulip}. 	

	\bibitem{}
		Peach, N. (1.941). The security Affiliates of National Banks. \emph{Baltimore: Johns Hopkins Press}.

	\bibitem{}
		Porter, M. (1.996). \emph{Competitive Strategy}. 

	\bibitem{}
		Posthumus, W. (1.929). The Tulip Mania in Holland in the Years 1.636 and 1.637. 	

	\bibitem{}
		Radelet, S., \& Sachs, J. (1.998). The Onset of the East Asian Financial Crisis. \emph{National Bureau of Economic Research, 6680}. 

	\bibitem{}
		Recuperado de \url{http://www.bde.es/f/webbde/Secciones/Publicaciones/InformesBoletinesRevistas/RevistaEstabilidadFinanciera/08/Nov/Fic/IEF200815.pdf}

	\bibitem{}
		Revistas Universitarias. (n.d.). Recuperado de \url{http://www.uclm.es/varios/revistas/docenciaeinvestigacion/numero3/hilario.asp}

	\bibitem{}
		Rivera Vega, C. M. (2.013, septiembre 10). Renta por comparación patrimonial | Gerencie.com [Web log post]. Recuperado de \url{http://www.gerencie.com/renta-por-comparacion-patrimonial.html}

	\bibitem{}
		Rodrigue, J.Recuperado de \url{http://people.hofstra.edu/jean-paul\_rodrigue/jpr\_blogs.html}

	\bibitem{}
		Saint-Paul, G. (1992). \emph{A Model of Labour Demand with Linear Adjustment Costs}.  

	\bibitem{}
		Samuelson, P. (1.958). An exact consumption-loan model of interest. \emph{The Journal of Political Economy, 76, 6}. 

	\bibitem{}
		Scherbina, A. (2.013). Asset Price Bubbles: A Selective Survey. \emph{IMF Working Paper}.  

	\bibitem{}
		Schama, S. (1.987). \emph{The Embarrassment of Riches}. 

	\bibitem{}
		Semper Augustus. (2.013). \emph{In Sir Thomas Browne}. Recuperado el 20 de junio de 2.013 de \url{http://penelope.uchicago.edu/~grout/encyclopaedia\_romana/aconite/semperaugustus.html}

	\bibitem{}
		Shiratsuka, S. (2.003). The asset price bubble in Japan in the 1980s: lessons for financial and macroeconomic stability. \emph{MF-BIS conference in Real Estate Indicators and Financial Stability 27-28 October}. 

	\bibitem{}
		Shiller, R. J. (2.000). \emph{Irrational Exuberance}. Princeton, NJ: Princeton University Press.

	\bibitem{}
		Smant, D. (2.001). Mississippi Bubble Dave Smant. Recuperado el 5 de octubre de 2.013 de \url{https://sites.google.com/site/davesmant/monetary-economics/famous-first-bubbles/mississippi-bubble}

	\bibitem{}
		Steiglitz, K., \& Shapiro, D. (1.998). Simulating the Madness of Crowds: Price Bubbles in an AuctionMediated Robot Market. \emph{Computational Economics, 12, 35–59}. 

	\bibitem{}
		Temin, P., \& Voth, H. (2.003). Riding the South Sea Bubble. Recuperado el 3 de febrero de 2.013 de \url{http://ssrn.com/abstract=485482}

	\bibitem{}
		Temin, P., \& Voth, H. (2.004). Riding the South Sea Bubble. 	

	\bibitem{}
		\emph{The Mississippi Bubble of 1718-1720} |. (n.d.). Recuperado el 11 de noviembre de 2.013 de \url{http://www.thebubblebubble.com/mississippi-bubble/}

	\bibitem{}
		Tirole, J. (1.982). \emph{On the Possibility of Speculation under Rational Expectations}. Econometrica. 
	

	\bibitem{}
		Thompson, A. E. (2.007, enero). The Tulipmania: Fact or Artifact? Recuperado el 10 de junio de 2.013 de \url{http://www.econ.ucla.edu/thompson/Document97.pdf}

	\bibitem{}
		Tulipmania [Video]. (2.008, mayo 28). Recuperado de \url{http://www.youtube.com/watch?v=QBE3Tbfqrg0}

	\bibitem{}
		Tulipmania Dave Smant. (2.013). Recuperado el 7 de agosto de 2.013 de \url{https://sites.google.com/site/davesmant/monetary-economics/famous-first-bubbles/tulipmania}

	\bibitem{}
		Tversky, A., \& Kahneman, D. (1.981). The Framing of Decisions and the Psychology of Choice. \emph{Science, 211}. 

	\bibitem{}
		Van Dijk, W. (1.951). Clusius observations on tulips has been collected in A Treatise on Tulips.

	\bibitem{}
		Van Horne, J. C. (1.985). Of Financial Innovations and Excesses. \emph{Journal of Finance}. 

	\bibitem{}
		Velde, F. R. (2.004). Government Equity and Money: John Law’s System in 1720 France. \emph{Federal Reserve Bank of Chicago}. 	

	\bibitem{}
		Walter, H., \& Walters, M. (2.001). \emph{Ein Garten Eden}. 	

	\bibitem{}
		What Are Economic Bubbles? - The dot.com Bubble [Video]. (2.011, julio 26). Recuperado el 15 de mayo de 2.013 de \url{http://www.youtube.com/watch?v=r1j\_AloLgQ8}

	\bibitem{}
		White, E. (1.990). The Stock Market Boom and Crash of 1929 Revisited. \emph{The Journal of Economic Perspectives, 4(2), 67-83}. 

	\bibitem{}
		Wolmar, C. (2.007). \emph{Fire \& Steam: A History of the Railways in Britain}. Atlantic Book.

	\bibitem{}
		Zorrilla, J. P. (2.010, junio 24). Contratos forwards | Gerencie.com [Web log post]. Recuperado el 7 de enero de 2.014 de \url{http://www.gerencie.com/contratos-forwards.html} 

	\bibitem{}
		Zuleta, Hernando (1.995); \emph{Impuesto inflacionario y señoreaje}, Borradores Semanales de Economía, Número: 38. Recuperado de \url{http://www.banrep.org/docum/ftp/borra038.pdf}

	\bibitem{}
		1.929 El Gran Crack [Video]. (n.d.). Recuperado de \url{http://www.youtube.com/watch?v=y80NRgYNPFA}

	\bibitem{}
		¿Que es una burbuja inmobiliaria? | Gerencie.com [Web log post]. (2013). Recuperado el 7 de enero de 2.014 de \url{http://www.gerencie.com/que-es-una-burbuja-inmobiliaria.html}

\end{thebibliography}
